---
title: "Lab 6"
output: word_document
---

```{r setup, include=FALSE}
library(tidyverse)
```

# Part 34 Lab 06: Join those tables! 

## 34.1 Exercise 1: singer 

```{r download data singer}

songs <- read_csv("https://raw.githubusercontent.com/bwiernik/progdata-class/master/data/singer/songs.csv")
locations <- read_csv("https://raw.githubusercontent.com/bwiernik/progdata-class/master/data/singer/loc.csv")

(time <- as_tibble(songs) |> 
   rename(song = title))

(album <- as_tibble(locations) |> 
   select(title, everything()) |> 
   rename(album = release,
          song  = title))

```

1 & 2. 
```{r songs and albums }
time_1 <- time |> 
  left_join(album, by = "song")
```

We know the corresponding album for songs 2-8, 11, 13, and 19-22 

3. 

```{r songs and year but not album}
time_2 <- time_1 |> 
  anti_join(album, by = "song")

```

We have a year, but not an album for: 
Corduroy, Martin_Doom!It's Seven O'Clock, Leaves And Sand, Comb Your Hair, Mine Again, Don't Forget About Us, Babydoll, and Vision of Love. 

4. 

```{r artists in time but not album}

time |> 
  anti_join(album, by = "artist_name")

```

Mariah Carey is in album but not time. 

5.

```{r two tibbles into 1 }
album_time <- album |> 
  left_join(time, by = "song")
```

Unsure how to merge the artist name columns

## 34.2 Exercise 2: LOTR 

```{r load data LOTR}
fell <- read_csv("https://raw.githubusercontent.com/jennybc/lotr-tidy/master/data/The_Fellowship_Of_The_Ring.csv")
ttow <- read_csv("https://raw.githubusercontent.com/jennybc/lotr-tidy/master/data/The_Two_Towers.csv")
retk <- read_csv("https://raw.githubusercontent.com/jennybc/lotr-tidy/master/data/The_Return_Of_The_King.csv")
```

1. 

```{r stack LOTR tibbles}

bind_rows(fell, retk, ttow)

```

2. 

```{r races fell}

fell |> 
  anti_join(retk, by = "Race") |> 
  anti_join(ttow, by = "Race")
  

```

All races are present in each movie. 

## 34.3 Set Operations

```{r load data set ops}
(y <-  tibble(x1 = LETTERS[1:3], x2 = 1:3))

(z <- tibble(x1 = c("B", "C", "D"), x2 = 2:4))
```

1. 
```{r intersect}

intersect(y, z)

```

x1: B, C with values x2: 2,3  

2. 

```{r mutate union }

union(
  mutate(y, day = "Day 1"),
  mutate(z, day = "Day 2")
)

```


3. 

```{r remove z}

setdiff(y, z)

```

