---
title: "Lab 02 - Plastic waste"
author: "Sabrina Eisenberg"
date: "1/27/2022"
output: html_document
---

## Load packages and data

```{r setup, message=FALSE}
library(tidyverse)
```

```{r load-data, message=FALSE}
plastic_waste <- read_csv(here::here("data", "plastic-waste.csv"))
```

## 17.3 Warm up 
Notice that some cells in the data have the value NA - what does this mean? 

This is where there are missing values 

## 17.4 Exercises

```{r plastic waste per cap dist}

ggplot(data = plastic_waste) +
  aes(x = plastic_waste_per_cap) +
  geom_histogram(binwidth = 0.2)

```

```{r filter greater than 3.5}
plastic_waste |>
  filter(plastic_waste_per_cap > 3.5)
```
This code finds the data points that are greater than the specified data point (3.5)

My brief research shows that Trinidad is a small island with many people that does not have a recycling system proportionate to its waste production. 

### 17.4.1 Exercise 1

1. 

```{r plastic-waste-continent}

ggplot(data = plastic_waste) +
  aes(x = plastic_waste_per_cap) +
  geom_histogram(binwidth = 0.2) + 
  facet_wrap (~continent)
  

```

It seems that most continents have low plastic waste per cap. It seems that North American and Asian countries have a wider range of plastic waste per cap, with North America having an outlier. It seems that, on average, Africa, Asia, Europe, and North America have similar plastic waste per cap. It is harder to compare the Oceania and South America because they have less data points. 


```{r plastic-waste-density}

ggplot(data = plastic_waste) +
  aes(x = plastic_waste_per_cap) +
  geom_density(aes(y = after_stat(count))) +
  facet_wrap(~continent)

```

2.

```{r plastic-waste-density-hist}

ggplot(data = plastic_waste) +
  aes(x = plastic_waste_per_cap, fill = continent, color = continent) +
  geom_density(aes(y = after_stat(count)), alpha = .3)

```

3. 

We define alpha level in the geom so that it applies to all arguments in the geom (global) and all layers. 

### 17.4.2 Exercise 2 

1. 

```{r plastic waste box}
ggplot(data = plastic_waste) +
  aes(x = continent,
      y = plastic_waste_per_cap,
      fill = continent) +
  geom_boxplot()
```

2. 
```{r boxplot with data }
ggplot(data = plastic_waste) +
  aes(x = continent,
      y = plastic_waste_per_cap,
      fill = continent) +
  geom_jitter(height = 0,
              width = .4) +
  geom_boxplot()
```

3. 

```{r plastic-waste raincloud}

ggplot(data = plastic_waste) +
  aes(x = continent,
      y = plastic_waste_per_cap,
      fill = continent) +
  geom_jitter(height = 0,
              width = .4) +
  geom_boxplot(color = "black",
               alpha = .5) +
    ggdist::stat_slab(height = .3,
                    color = "black",
                    size = .2,
                    alpha = .5,
                    position = position_nudge(y = .2))

```

4. The density plot and jitter show the distribution of the data points better than the box plot. It accounts more for outliers as well. 

### 17.4.3 Exercise 3 

1. 


```{r plastic-waste-mismanaged}

ggplot(data = plastic_waste) +
  aes(x = plastic_waste_per_cap,
      y = mismanaged_plastic_waste_per_cap) +
  geom_point()

```

It seems like there is a positive relationship between the two variables with increasing variability. 

2. 

```{r plastic-waste-mismanaged-continent}

ggplot(data = plastic_waste) +
  aes(x = plastic_waste_per_cap,
      y = mismanaged_plastic_waste_per_cap, color = continent) +
  geom_point()

```

There seems to be a steeper positive relationship for Africa and Asia. North America, Europe, and Oceana seem to have more variability. Europe and North America's positive relationship seems to have a smaller slope.

3. 


```{r plastic-waste-population-total}

ggplot(data = plastic_waste) +
  aes(x = total_pop,
      y = plastic_waste_per_cap) +
  geom_point() +
  geom_smooth()

```

```{r plastic-waste-population-coastal}

ggplot(data = plastic_waste) +
  aes(x = coastal_pop,
      y = plastic_waste_per_cap) +
  geom_point() +
  geom_smooth()


```


It is hard to tell with the outliers, but it seems like the coastal population graph has a stronger association 


### Exercise 8

Remove this text, and add your answer for Exercise 8 here.

```{r recreate-viz}
# insert code here
```

## Pro-Tips

### Excercise 3

Try this :D

```
ggplot(data = plastic_waste, 
       mapping = aes(x = continent, 
                     y = plastic_waste_per_cap)) +
  geom_violin()+
  geom_boxplot(width=.3, fill="green") +
  stat_summary(fun.y=median, geom="point") 
```

### Exercise 5 

Helpful reference:http://www.sthda.com/english/wiki/ggplot2-themes-and-background-colors-the-3-elements
