---
title: "Lab 02 - Plastic waste"
author: "Sabrina Eisenberg"
date: "1/27/2022"
output: html_document
---

## Load packages and data

```{r setup, message=FALSE}
library(tidyverse)
```

```{r load-data, message=FALSE}
plastic_waste <- read_csv(here::here("data", "plastic-waste.csv"))
```

## Warm up 
Notice that some cells in the data have the value NA - what does this mean? 

This is where there are missing values 

## Exercises

```{r plastic waste per cap dist}

ggplot(data = plastic_waste) +
  aes(x = plastic_waste_per_cap) +
  geom_histogram(binwidth = 0.2)

```

```{r filter greater than 3.5}
plastic_waste |>
  filter(plastic_waste_per_cap > 3.5)
```
This code finds the data points that are greater than the specified data point (3.5)

My brief research shows that Trinidad is a small island with many peopel that does not have a recycling system proportionate to its waste production. 

### Exercise 1


```{r plastic-waste-continent}

ggplot(data = plastic_waste) +
  aes(x = plastic_waste_per_cap) +
  geom_histogram(binwidth = 0.2) + 
  facet_wrap (~continent)
  

```

### Exercise 2

```{r plastic-waste-density}
# insert code here
```

### Exercise 3

Remove this text, and add your answer for Exercise 3 here.

### Exercise 4

Remove this text, and add your answer for Exercise 4 here.

```{r plastic-waste-violin}
# insert code here
```

### Exercise 5

Remove this text, and add your answer for Exercise 5 here.

```{r plastic-waste-mismanaged}
# insert code here
```

### Exercise 6

Remove this text, and add your answer for Exercise 6 here.

```{r plastic-waste-mismanaged-continent}
# insert code here
```

### Exercise 7

Remove this text, and add your answer for Exercise 7 here.

```{r plastic-waste-population-total}
# insert code here
```

```{r plastic-waste-population-coastal}
# insert code here
```

### Exercise 8

Remove this text, and add your answer for Exercise 8 here.

```{r recreate-viz}
# insert code here
```

## Pro-Tips

### Excercise 3

Try this :D

```
ggplot(data = plastic_waste, 
       mapping = aes(x = continent, 
                     y = plastic_waste_per_cap)) +
  geom_violin()+
  geom_boxplot(width=.3, fill="green") +
  stat_summary(fun.y=median, geom="point") 
```

### Exercise 5 

Helpful reference:http://www.sthda.com/english/wiki/ggplot2-themes-and-background-colors-the-3-elements
